Explore Vegetation Data

### 2016-02-17 explore_veg_data.Rmd
Revise species names.

veg_us <- as.tbl(veg_us)
veg_us
veg_us$UnderstorySp <- tolower(veg_us$UnderstorySp)
summary(veg_us)
unique(veg_us$UnderstorySp)
# summary(filter(veg_us, UnderstorySp == "None"))
# summary(filter(veg_us, UnderstorySp == "OPEN"))
veg_us[veg_us == -9999] <- NA
veg_us$UnderstorySp[veg_us$UnderstorySp == "none"] <- "open"
veg_us$UnderstorySp[veg_us$UnderstorySp == "arcto sp."] <- "arcto"
filter(veg_us, UnderstorySp == "vasp")

@@

veg_us$UnderstorySp[veg_us$UnderstorySp == "vinca sp"] <- "vinca sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "lusp" | veg_us$UnderstorySp == "lupinus sp"] <- "lupine sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "vasp"] <- "vaccinium sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "gasp"] <- "garrya sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "qusp"] <- "quercus sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "risp" | veg_us$UnderstorySp == "ribes sp"] <- "ribes sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "prunus sp"] <- "prunus sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "rosa" | veg_us$UnderstorySp == "rosp"] <- "rose sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "rubu sp."] <- "rusp"
veg_us$UnderstorySp[veg_us$UnderstorySp == "rhsp"] <- "rhamnus sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "garry sp."] <- "garrya sp."

@@

veg_us_summ <- mutate(veg_us_summ, pcov = ptct/totpts)
veg_us_summ
summary(veg_us_summ)
unique(veg_us_summ$UnderstorySp)

>>>>

veg_us <- as.tbl(veg_us)
veg_us
veg_us$UnderstorySp <- tolower(veg_us$UnderstorySp)
summary(veg_us)
unique(veg_us$UnderstorySp)
# summary(filter(veg_us, UnderstorySp == "None"))
# summary(filter(veg_us, UnderstorySp == "OPEN"))
veg_us[veg_us == -9999] <- NA
veg_us$UnderstorySp[veg_us$UnderstorySp == "none"] <- "open"
veg_us$UnderstorySp[veg_us$UnderstorySp == "arcto sp." | veg_us$UnderstorySp == "arma"] <- "arcto"
filter(veg_us, UnderstorySp == "vasp")

@@

veg_us$UnderstorySp[veg_us$UnderstorySp == "vinca sp"] <- "vinca sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "lusp" | veg_us$UnderstorySp == "lupinus sp"] <- "lupine sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "vasp"] <- "vaccinium sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "gasp"] <- "garrya sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "qusp"] <- "quercus sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "risp" | veg_us$UnderstorySp == "ribes sp"] <- "ribes sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "prunus sp"] <- "prunus sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "rosa" | veg_us$UnderstorySp == "rosp"] <- "rose sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "rubu sp."] <- "rusp"
veg_us$UnderstorySp[veg_us$UnderstorySp == "rhsp"] <- "rhamnus sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "garry sp."] <- "garrya sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "rose sp."] <- "rosa sp."
veg_us$UnderstorySp[veg_us$UnderstorySp == "ribes sp."] <- "ribes"

@@

veg_us_summ <- mutate(veg_us_summ, pcov = ptct/totpts)
veg_us_summ
summary(veg_us_summ)
sort(unique(veg_us_summ$UnderstorySp))
